%------------------------------------
% Typesetting style by: Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,letterpaper,sans]{moderncv}

\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{black}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
\usepackage{etaremune}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}


\usepackage[scale=0.75]{geometry}

% To add the footer
\pagestyle{fancy}
\fancyhf{}
\cfoot{Doup\'e---\thepage}

% Change the styling of the subsection to add more spacing
\makeatletter
\RenewDocumentCommand{\subsection}{sm}{%
  \par\addvspace{2ex}%
  \phantomsection{}% reset the anchor for hyperrefs
  \addcontentsline{toc}{subsection}{#2}%
  \cvitem[0ex]{}{\strut\subsectionstyle{\textbf{#2}}}%
  \par\nobreak\addvspace{2ex}\@afterheading}% to avoid a pagebreak after the heading
\makeatother

\widowpenalty=10000
\clubpenalty=10000



\name{Adam}{Doup\'e}
\address{P.O. Box 878809}{Tempe, AZ 85287-8809}
\phone[fixed]{480-727-5471}
\email{doupe@asu.edu}
\homepage{adamdoupe.com}

\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother


% DOCUMENT
\begin{document}
\makecvtitle

\section{Education}
\cventry{2010--2014}{PhD in Computer Science}{University of California, Santa
  Barbara}{}{}{Advisors: Giovanni Vigna and
  Christopher Kruegel\\
  Thesis: Advanced Automated Web Application Vulnerability Analysis
}  % arguments 3 to 6 can be left empty
\cventry{2008--2009}{Master's Degree in Computer Science}{University of California, Santa
  Barbara}{}{}{Advisor: Giovanni Vigna \\
  Topic: Black Box Web Vulnerability Scanners
}  % arguments 3 to 6 can be left empty
\cventry{2004--2008}{Bachelor's Degree in Computer Science with Honors}{University of California, Santa
  Barbara}{}{}{}  % arguments 3 to 6 can be left empty

\section{Professional Appointments}


\cventry{2020--Present}{Associate Professor}{Arizona State
  University}{}{}{}

\cventry{2021--Present}{Director}{Center for Cybersecurity
  and Trusted Foundations}{Arizona State
  University}{}{}

\cventry{2020--2021}{Acting Director}{Center for Cybersecurity
  and Trusted Foundations}{Arizona State
  University}{}{}

\cventry{2017--2020}{Associate Director}{Center for Cybersecurity
  and Trusted Foundations}{Arizona State
  University}{}{}

\cventry{2014--2020}{Assistant Professor}{Arizona State
  University}{}{}{}

\section{Research Funding}

\begin{etaremune}

\item DARPA 2024--2026. \textit{American Cybersecurity Education (ACE) Institute,} \$4,462,558, co-PI (w/ Yan Shoshitaishvili as PI and Fish Wang and Tiffany Bao as co-PIs), share \$1,115,639.

\item NSA 2024--2029. \textit{STEEDDEMON: Human-assisted Cyber Reasoning Systems,} \$2,496,407, co-PI (w/ Yan Shoshitaishvili as PI and Chitta Baral as co-PI), share \$998,562.

\item Stony Brook University 2024--2027. \textit{ONR: Tools and Techniques for Characterizing Integrity in DevOps Technologies,} \$300,001, PI, share \$300,001.

\item DARPA 2024. \textit{STTR: SENSEI: Scaling Education Nationwide for Security Expertise and Impact,} \$82,234, co-PI (w/ Yan Shoshitaishvili as PI).

\item ARPA-H 2024--2024. \textit{RxCRS: Reliable and eXplainable Cyber Reasoning System for Digital Health Security,} \$10,186,189, co-PI (w/ Fish Wang as PI and Tiffany Bao, Kenneth Buetow, Stephanie Forrest, Duong Nguyen, Yan Shoshitaishvili, and Ni Trieu as co-PIs), share \$1,833,514.

\item DARPA 2023--2027. \textit{SENPAI: Strategic Exploration, Navigation, and Patching of Abstracted Integration,} \$7,960,690, co-PI (w/ Tiffany Bao as PI and Sandeep Gupta, Zilin Jiang, Giulia Pedrielli, Yan Shoshitaishvili, and Ruoyu Wang as co-PIs), share \$1,990,172.

\item NSA 2023--2026. \textit{SoS: Leveraging Machine Learning for Binary Software Understanding,} \$748,949, co-PI (w/ Yan Shoshitaishvili as PI and Chitta Baral as co-PI), share \$441,678.  

\item ARO 2023--2024. \textit{DURIP: Next Generation Machine Learning Platform for Advanced Vulnerability Analysis and Reverse Engineering,} \$209,283, co-PI (w/ Yan Shoshitaishvili as PI and Tiffany Bao as co-PI), share \$52,320.
  
\item Ripple 2022--2023. \textit{Ripple Impact Fund,} \$34,999, PI.
  
\item PayPal 2022--2023. \textit{Protecting the online ecosystem through proactive cybercrime reporting,} \$100,001, PI.

\item NSA 2022--2024. \textit{Human-Assisted Cyber Reasoning Systems Cont.,} \$2,178,001, co-PI (w/ Yan Shoshitaishvili PI and Chitta Baral as co-PI), share \$990,000.
  
\item DARPA 2022--2026. \textit{\textsc{Euryale}: Combating Emergent Execution with UTE,} \$3,768,945, PI, (w/ Fish Wang, Yan Shoshitaishvili, Tiffany Bao, Stephanie Forrest, and Giulia Pedrielli as co-PIs), share \$1,130,683.

\item ONR 2020--2023. \textit{Tools and Techniques to Improve the Granularity and Usability of Web Application,} \$1,599,983, PI.

  \item DARPA 2020--2024. \textit{DARPA AMP: VOLT: A Viscous, Orchestrated Lifting and Translation Framework,} \$6,678,767, co-PI (w/ Fish Wang PI and Tiffany Bao, Georgios Fainekos, Stephanie Forrest, Sandeep Gupta, and Yan Shoshitaishvili as co-PIs), share \$1,001,815.

  \item NSA 2019--2021. \textit{Human-Assisted Cyber Reasoning Systems,} \$1,299,053, co-PI (w/ Yan Shoshitaishvili PI and Tiffany Bao as co-PI), share \$436,703.

  \item IBM 2019--2022. \textit{DARPA CHASE: Hardened Orchestrated Response for Uncertain Settings (HORUS),} \$674,083, PI (w/ Subbarao Kambhampati co-PI), share \$337,041.

  \item DARPA 2019--2022. \textit{DARPA CHESS: CHECRS: Cognitive Human Enhancements for Cyber Reasoning Systems,} \$11,730,557, co-PI (w/ Fish Wang PI and Yan Shoshitaishvili PI and Tiffany Bao, Chitta Baral, and Stephanie Forrest as co-PIs), share \$1,524,972.

  \item DARPA 2018--2022. \textit{DARPA HACCS: Puppeteer---Achieving Remote Control Over Complex Systems,} \$7,474,245, co-PI (w/ Yan Shoshitaishvili PI), share \$1,868,561.

  \item NSF 2018--2023. \textit{NSF ADVANCE: ASU ADVANCE Institutional Transformation,} \$2,999,743, Co-Investigator (w/ Elizabeth Wentz as PI), share \$29,997.

  \item NSF 2017--2022. \textit{NSF-SFS: Arizona Cyber Defense
    Scholarship,} \$3,997,784, co-PI (w/ Gail-Joon Ahn PI and Steven
    Yau, Ziming Zhao, and Dijiang Huang co-PIs), share \$399,778.

  \item NSF 2017--2021. \textit{SaTC: CORE: Medium: Collaborative:
    Taming Web Content Through Automated Reduction in Browser
    Functionality,} \$406,080, PI.

  \item Soongsil University 2017--2024. \textit{Automatic Deep Malware
    Analysis Technology for Cyber Threat Intelligence,} \$708,160,
    co-PI (w/ Gail-Joon Ahn PI), share \$283,264.

  \item ONR 2017--2019. \textit{XS-Shredder: A Cross-Layer Framework
    for Removing Code Bloat in Web Applications,} \$1,230,547, PI.

  \item NSF 2017--2022. \textit{CAREER: Next Generation Black-Box Web
    Application Vulnerability Analysis,} \$416,585, PI.

  \item NSF 2016--2019. \textit{Collaborative Research: CICI: Secure
    and Resilient Architecture: SciGuard: Building a Security
    Architecture for Science DMZ based on SDN and NFV Technologies,}
    \$499,484, co-PI (w/ Gail-Joon Ahn PI and Dijiang Huang co-PI),
    share \$149,845.

  \item NSF 2016--2018. \textit{EDU: Collaborative: Educating the
    Security Workforce through On-Demand Live Competitions,}
    \$154,643, PI (w/ Gail-Joon Ahn co-PI), share \$77,321.

  \item ONR 2015. \textit{Academic Survey of the Cyber Resiliency of
    the Total Embedded Systems Platform,} \$49,998, PI.

\end{etaremune}

\section{Honors and Awards}

\cventry{2021}{Best Student Paper Award}{IEEE Symposium on Security and Privacy}{}{}{}{}

\cventry{2020}{Second Place Internet Defense Prize}{Facebook}{}{}{}{}

\cventry{2020}{Distinguished Paper Award}{USENIX Security Symposium (USENIX)}{}{}{}{}

\cventry{2019}{Distinguished Paper Award}{USENIX Security Symposium (USENIX)}{}{}{}{}

\cventry{2019}{Fulton Schools of Engineering Best Teacher Award---Top
  5\%}{Arizona State University}{}{}{}

\cventry{2018}{Fulton Schools of Engineering Best Teacher Award}{Arizona State University}{}{}{}{}

\cventry{2017}{Fulton Outstanding Assistant Professor}{Arizona State University}{}{}{}{}

\cventry{2017}{Fulton Schools of Engineering Best Teacher Award}{Arizona State University}{}{}{}{}

\cventry{2017}{NSF CAREER Award}{}{}{}{}{}

\cventry{2016}{Best Paper Award}{Toward Authenticated Caller ID
  Transmission: The Need for a Standardized Authentication Scheme in
  Q.731.3 Calling Line Identification Presentation}{ITU Kaleidoscope}{}{}{}

\cventry{2016}{Fulton Schools of Engineering Best Teacher Award---Top
  5\%}{Arizona State University}{}{}{}

\cventry{2015}{Best Paper Award}{A Large-Scale Study of Mobile Web App
  Security}{Mobile Security Technologies Workshop}{}{}{}

\cventry{2013}{Outstanding Publication Award in Computer
  Science}{Enemy of the State: A State-Aware Black-Box Web
  Vulnerability Scanner}{University of California, Santa Barbara}{}{}

\cventry{2011}{Outstanding Teaching Assistant Award}{CS
  279---(Graduate) Network Security and Intrusion
  Detection}{University of California, Santa Barbara}{}{}

\cventry{2010}{Gold Star Award}{Microsoft}{}{}{}

\cventry{2009}{Outstanding Teaching Assistant Award}{CS 177---Introduction to Computer Security}{University of California, Santa Barbara}{}{}


\section{Publications}

Students advised, co-advised, or mentored are underlined,
undergraduate students contain an asterisk next to their name, and
conference acceptance rates are provided when available. First
authorship indicates primary contribution, unless otherwise noted.

\subsection{Journal Papers (refereed)}

\begin{etaremune}

\item Pemma Reiter, \underline{Hui Jun Tay},  Westley Weimer,  \textbf{Adam Doup\'e},  Ruoyu Wang, and  Stephanie Forrest, ``Automatically Mitigating Vulnerabilities in Binary Programs via Partially Recompilable Decompilation,'' in \emph{IEEE Transactions on Dependable and Secure Computing}, October, 2024.

\item Edward Schrom, Ann Kinzig, Stephanie Forrest, Andrea L. Graham, Simon A. Levin, Carl T. Bergstrom, Carlos Castillo-Chavez, James P. Collins, Rob J. de Boer, \textbf{Adam Doup\'e}, Roya Ensafi, Stuart Feldman, Bryan T. Grenfell, J. Alex Halderman, Silvie Huijben, Carlo Maley, Melanie Moses, Alan S. Perelson, Charles Perrings, Joshua Plotkin, Jennifer Rexford, and Mohit Tiwari, ``Challenges in cybersecurity: Lessons from biological defense systems,'' in \emph{Mathematical Biosciences}, June, 2023.

\item \underline{Huahong Tu}, \textbf{Adam Doup\'e}, Ziming Zhao, and
  Gail-Joon Ahn, ``Toward Standardization of Authenticated Caller ID
  Transmission,'' in \emph{IEEE Communications Standards Magazine},
    1(3), pp. 30-36, October 2017.

\item \underline{Sai Prashanth Chandramouli}, Ziming Zhao,
  \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``E-mail Header Injection
  Vulnerabilities,'' in \emph{it - Information Technology}, 59(2), pp.
  67-72, March 2017.

\end{etaremune}

\subsection{Conference Papers with Proceedings (refereed)}

\begin{etaremune}

\item \underline{Marzieh Bitaab}, \underline{Alireza Karimi}, \underline{Zhuoer Lyu}, \underline{Ahmadreza Mosallanezhad}, Adam Oest, Ruoyu Wang, Tiffany Bao, Yan Shoshitaishvili, and \textbf{Adam Doup\'e}, ``ScamNet: Toward Explainable Large Language Model-based Fraudulent Shopping Website Detection,'' in \emph{Proceedings of the AAAI Conference on Artificial Intelligence (AAAI)}, February, 2025.

\item \underline{Marzieh Bitaab}, \underline{Alireza Karimi}, \underline{Zhuoer Lyu}, Adam Oest, Dhruv Kuchhal, Muhammad Saad, Gail-Joon Ahn, Ruoyu Wang, Tiffany Bao, Yan Shoshitaishvili, and \textbf{Adam Doup\'e}, ``ScamMagnifier: Piercing the Veil of Fraudulent Shopping Website Campaigns,'' in \emph{Proceedings of the Symposium on Network and Distributed System Security (NDSS)}, February, 2025.

\item \underline{Faezeh Kalantari}, \underline{Mehrnoosh Zaeifi}, \underline{Yeganeh Safaei}, \underline{Marzieh Bitaab}, Adam Oest, Gianluca Stringhini, Yan Shoshitaishvili, and \textbf{Adam Doup\'e}, ``Browser Polygraph: Efficient Deployment of Coarse-Grained Browser Fingerprints for Web-Scale Detection of Fraud Browsers,'' in \emph{Proceedings of the ACM Internet Measurement Conference (IMC)}, November, 2024.

\item \underline{Arvind S Raj}, \underline{Wil Gibbs}, \underline{Fangzhou Dong}, \underline{Jayakrishna Vadayath}, \underline{Michael Tompkins}, \underline{Steven Wirsz}, \underline{Yibo Liu}, Zhenghao Hu, \underline{Chang Zhu}, Gokulkrishna Praveen Menon, Brendan Dolan-Gavitt, \textbf{Adam Doup\'e}, Ruoyu Wang, Yan Shoshitaishvili, and Tiffany Bao, ``Fuzz to the Future: Uncovering Occluded Future Vulnerabilities via Robust Fuzzing,'' in \emph{Proceedings of the ACM Conference on Computer and Communications Security (CCS)}, October, 2024.

\item \underline{Zhibo Sun}, \underline{Faris Bugra Kokulu}, \underline{Penghui Zhang}, Adam Oest, Gianluca Stringhini, Tiffany Bao, Ruoyu Wang, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``From Victims to Defenders: An Exploration of the Phishing Attack Reporting Ecosystem,'' in \emph{Proceedings of the International Symposium on Research in Attacks, Intrusions and Defenses (RAID)}, September, 2024.

\item \underline{Zion Leonahenahe Basque}, \underline{Ati Priya Bajaj}, \underline{Wil Gibbs}, \underline{Jude O'Kain}, Derron Miao, Tiffany Bao, \textbf{Adam Doup\'e}, Yan Shoshitaishvili, and Ruoyu Wang, ``Ahoy SAILR! There is No Need to DREAM of C: A Compiler-Aware Structuring Algorithm for Binary Decompilation,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2024.

\item \underline{Ananta Soneji}, Vaughn Hamilton, \textbf{Adam Doup\'e}, Allison McDonald, and Elissa M. Redmiles, ``"I feel physically safe but not politically safe": Understanding the Digital Threats and Safety Practices of OnlyFans Creators,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2024.

\item \underline{Wil Gibbs}, \underline{Arvind S Raj}, \underline{Jayakrishna Vadayath}, \underline{Hui Jun Tay}, \underline{Justin Miller}, \underline{Akshay Ajayan}, \underline{Zion Leonahenahe Basque}, Audrey Dutcher, Fangzhou Dong, \underline{Xavier J. Maso}, Giovanni Vigna, Christopher Kruegel, \textbf{Adam Doup\'e}, Yan Shoshitaishvili, and Ruoyu Wang, ``Operation Mango: Scalable Discovery of Taint-Style Vulnerabilities in Binary Firmware Services,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2024.

\item Eric Olsson, Benjamin Eriksson, \textbf{Adam Doup\'e}, and Andrei Sabelfeld, ``Spider-Scents: Grey-box Database-aware Web Scanning for Stored XSS,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2024.

\item Ziyi Guo, Dang K Le, Zhenpeng Lin, \underline{Kyle Zeng}, Ruoyu Wang, Tiffany Bao, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, and Xinyu Xing, ``Take a Step Further: Understanding Page Spray in Linux Kernel Exploitation,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2024.

\item \underline{Chang Zhu}, Ziyang Li, Anton Xue, \underline{Ati Priya Bajaj}, \underline{Wil Gibbs}, \underline{Yibo Liu}, Rajeev Alur, Tiffany Bao, Hanjun Dai, \textbf{Adam Doup\'e}, Mayur Naik, Yan Shoshitaishvili, Ruoyu Wang, and Aravind Machiry, ``TYGR: Type Inference on Stripped Binaries using Graph Neural Networks,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2024.

\item \underline{Vivin Paliath}, \underline{Erik Trickel}, Tiffany Bao, Ruoyu Wang, \textbf{Adam Doup\'e}, and Yan Shoshitaishvili, ``SandPuppy: Deep-State Fuzzing Guided by Automatic Detection of State-Representative Variables,'' in \emph{Proceedings of the Conference on Detection of Intrusions and Malware {\&} Vulnerability Assessment (DIMVA)}, July, 2024.

\item \underline{Rana Pourmohamad}, \underline{Steven Wirsz}, Adam Oest, Tiffany Bao, Yan Shoshitaishvili, Ruoyu Wang, \textbf{Adam Doup\'e}, and Rida A. Bazzi, ``Deep Dive into Client-Side Anti-Phishing: A Longitudinal Study Bridging Academia and Industry,'' in \emph{Proceedings of the ACM Symposium on Information, Computer and Communications Security (AsiaCCS)}, July, 2024.

\item \underline{Mehrnoosh Zaeifi}, \underline{Faezeh Kalantari}, Adam Oest, \underline{Zhibo Sun}, Gail-Joon Ahn, Yan Shoshitaishvili, Tiffany Bao, Ruoyu Wang, and \textbf{Adam Doup\'e}, ``Nothing Personal: Understanding the Spread and Use of Personally Identifiable Information in the Financial Ecosystem,'' in \emph{Proceedings of the ACM on Conference on Data and Application Security and Privacy (CODASPY)}, June, 2024.

\item Kuntal Kumar Pal$^*$, \underline{Ati Priya Bajaj}$^*$, Pratyay Banerjee, Audrey Dutcher, Mutsumi Nakamura, \underline{Zion Leonahenahe Basque}, Himanshu Gupta, Saurabh Arjun Sawant, Ujjwala Anantheswaran, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, Chitta Baral, and Ruoyu Wang, ``"Len or index or count, anything but v1": Predicting Variable Names in Decompilation Output with Transfer Learning,'' in \emph{Proceedings of the IEEE Symposium on Security and Privacy}, May, 2024. \\
  $^*$Co-first authors

\item \underline{Irina Ford}, \underline{Ananta Soneji}, \underline{Faris Bugra Kokulu}, \underline{Jayakrishna Vadayath}, \underline{Zion Leonahenahe Basque}, Gaurav Vipat, \textbf{Adam Doup\'e}, Ruoyu Wang, Gail-Joon Ahn, Tiffany Bao, and Yan Shoshitaishvili, ``"Watching over the shoulder of a professional": Why Hackers Make Mistakes and How They Fix Them,'' in \emph{Proceedings of the IEEE Symposium on Security and Privacy}, May, 2024.

\item \underline{Kyle Zeng}, Zhenpeng Lin, Kangjie Lu, Xinyu Xing, Ruoyu Wang, \textbf{Adam Doup\'e}, Yan Shoshitaishvili, and Tiffany Bao, ``RetSpill: Igniting User-Controlled Data to Burn Away Linux Kernel Protections,'' in \emph{Proceedings of the ACM Conference on Computer and Communications Security (CCS)}, November 2023.

\item \underline{Hui Jun Tay}, \underline{Kyle Zeng}, \underline{Jayakrishna Vadayath}, \underline{Arvind S Raj}, \underline{Audrey Dutcher}, \underline{Tejesh Reddy}, \underline{Wil Gibbs}, \underline{Zion Leonahenahe Basque}, \underline{Fangzhou Dong}, \underline{Zack Smith}, \textbf{Adam Doup\'e}, Tiffany Bao, Yan Shoshitaishvili, and Ruoyu Wang, ``Greenhouse: Single-Service Rehosting of Linux-Based Firmware Binaries in User-Space Emulation,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2023.

\item Jaejong Baek, \underline{Pradeep Kumar Duraisamy Soundrapandian}, \underline{Sukwha Kyung}, Ruoyu Wang, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``Targeted Privacy Attacks by Fingerprinting Mobile Apps in LTE Radio Layer,'' in \emph{Proceedings of the IEEE/IFIP International Conference on Dependable Systems and Networks (DSN)}, June, 2023.
  
\item \underline{Marzieh Bitaab}, Haehyun Cho, Adam Oest, \underline{Zhuoer Lyu}, Wei Wang, Jorij Abraham, Ruoyu Wang, Tiffany Bao, Yan Shoshitaishvili, and \textbf{Adam Doup\'e}, ``Beyond Phish: Toward Detecting Fraudulent e-Commerce Websites at Scale,'' in \emph{Proceedings of the IEEE Symposium on Security and Privacy}, May 2023.

\item \underline{Erik Trickel},  Fabio Pagani, \underline{Chang Zhu}, Lukas Dresel,  Giovanni Vigna,  Christopher Kruegel, Ruoyu Wang,  Tiffany Bao,  Yan Shoshitaishvili, and  \textbf{Adam Doup\'e}, ``Toss a Fault to Your Witcher: Applying Grey-box Coverage-Guided Mutational Fuzzing to Detect SQL and Command Injection Vulnerabilities,'' in \emph{Proceedings of the IEEE Symposium on Security and Privacy}, May, 2023.

\item \underline{Penghui Zhang},  \underline{Zhibo Sun}, \underline{Sukwha Kyung},  Hans Walter Behrens,  \underline{Zion Leonahenahe Basque}, Haehyun Cho,  Adam Oest,  Ruoyu Wang,  Tiffany Bao,  Yan Shoshitaishvili,  Gail-Joon Ahn, and \textbf{Adam Doup\'e}, ``I'm Spartacus, No, I'm Spartacus: Proactively Protecting Users from Phishing by Intentionally Triggering Cloaking Behavior,'' in \emph{Proceedings of the ACM Conference on Computer and Communications Security (CCS)}, November, 2022.

\item \underline{Faezeh Kalantari}, \underline{Mehrnoosh Zaeifi},  Tiffany Bao,  Ruoyu Wang,  Yan Shoshitaishvili, and  \textbf{Adam Doup\'e}, ``Context-Auditor: Context-sensitive Content Injection Mitigation,'' in \emph{Proceedings of the International Symposium on Research in Attacks, Intrusions and Defenses (RAID)}, October, 2022.
  
\item Siddhant Bhambri$^*$,  \underline{Purv Chauhan}$^*$,  Frederico Araujo,  \textbf{Adam Doup\'e}, and  Subbarao Kambhampati, ``Using Deception in Markov Game to Understand Adversarial Behaviors through a Capture-The-Flag Environment,'' in \emph{Proceedings of the Conference on Decision and Game Theory for Security (GameSec)}, October, 2022. \\
  $^*$Co-first authors
  
  
\item Soroush Karami$^*$,  \underline{Faezeh Kalantari}$^*$, \underline{Mehrnoosh Zaeifi},  \underline{Xavier J. Maso},  \underline{Erik Trickel},  Panagiotis Ilia,  Yan Shoshitaishvili,  \textbf{Adam Doup\'e}, and  Jason Polakis, ``Unleash the Simulacrum: Shifting Browser Realities for Robust Extension-Fingerprinting Prevention,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2022. \\
  $^*$Co-first authors
  
\item \underline{Jayakrishna Vadayath},  Moritz Eckert,  \underline{Kyle Zeng},  Nicolaas Weideman,  Gokulkrishna Praveen Menon,  Yanick Fratantonio,  Davide Balzarotti,  \textbf{Adam Doup\'e},  Tiffany Bao,  Ruoyu Wang, Christophe Hauser, and  Yan Shoshitaishvili, ``Arbiter: Bridging the Static and Dynamic Divide in Vulnerability Discovery on Binary Programs,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2022.
  
\item \underline{Kyle Zeng}$^*$,  Yueqi Chen$^*$,  Haehyun Cho,  Xinyu Xing,  \textbf{Adam Doup\'e},  Yan Shoshitaishvili, and Tiffany Bao, ``Playing for K(H)eaps: Understanding and Improving Linux Kernel Exploit Reliability,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2022. \\
  $^*$Co-first authors

\item Pemma Reiter$^*$,  Antonio M. Espinoza$^*$,  \textbf{Adam Doup\'e},  Ruoyu Wang,  Westley Weimer, and Stephanie Forrest, ``Improving Source-Code Representations to Enhance Search-based Software Repair,'' in \emph{Proceedings of the Genetic and Evolutionary Computation Conference (GECCO)}, July, 2022. \\
  $^*$Co-first authors
  
\item \underline{Ananta Soneji},  \underline{Faris Bugra Kokulu},  Carlos E. Rubio-Medrano,  Tiffany Bao,  Ruoyu Wang,  Yan Shoshitaishvili, and  \textbf{Adam Doup\'e}, ``"Flawed, but like democracy we don't have a better system": The Experts' Insights on the Peer Review Process of Evaluating Security Papers,'' in \emph{Proceedings of the IEEE Symposium on Security and Privacy}, May, 2022.
  
\item Rock Stevens$^*$,  \underline{Faris Bugra Kokulu}$^*$,  \textbf{Adam Doup\'e}, and  Michelle Mazurek,  ``Above and Beyond: Organizational Efforts to Complement U.S. Digital Security Compliance Mandates,'' in \emph{Proceedings of the Symposium on Network and Distributed System Security (NDSS)}, February, 2022. \\
  $^*$Co-first authors
  
\item \underline{Haehyun Cho}, Jinbum Park, Adam Oest, Tiffany Bao,  Ruoyu Wang,  Yan Shoshitaishvili,  \textbf{Adam Doup\'e}, and  Gail-Joon Ahn, ``ViK: Practical Mitigation of Temporal Memory Safety Violations through Object ID Inspection,'' in \emph{Proceedings of the ACM International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS)}, February, 2022.

\item \underline{Zhibo Sun}, \underline{Adam Oest}, \underline{Penghui Zhang}, Carlos E. Rubio-Medrano, Tiffany Bao, Ruoyu (Fish) Wang, Ziming Zhao, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``Having Your Cake and Eating It: An Analysis of Concession-Abuse-as-a-Service,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, August, 2021.

\item \underline{Penghui Zhang}, \underline{Adam Oest}, \underline{Haehyun Cho}, \underline{Zhibo Sun}, RC Johnson, Brad Wardman, Shaown Sarker, Alexandros Kapravelos, Tiffany Bao, Ruoyu (Fish) Wang, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``CrawlPhish: Large-scale Analysis of Client-side Cloaking Techniques in Phishing,'' in \emph{Proceedings of the IEEE Symposium on Security and Privacy}, May, 2021. \\
  \textbf{Best Student Paper Award}

\item \underline{Jaswant Pakki}, Yan Shoshitaishvili, Ruoyu Wang, Tiffany Bao, and \textbf{Adam Doup\'e}. ``Everything You Ever Wanted to Know About Bitcoin Mixers (But Were Afraid to Ask),'' in \emph{Proceedings of the Financial Cryptography and Data Security Conference}, March, 2021. 

\item \underline{Sung Ta Dinh}, \underline{Haehyun Cho}, Kyle Martin, Adam Oest, \underline{Kyle Zeng}, Alexandros Kapravelos, Gail-Joon Ahn, Tiffany Bao, Ruoyu Wang, \textbf{Adam Doup\'e}, and Yan Shoshitaishvili, ``Favocado: Fuzzing the Binding Code of JavaScript Engines Using Semantically Correct Test Cases,'' in \emph{Proceedings of the ISOC Network and Distributed System Security Symposium (NDSS)}, February, 2021.

\item Frederico Araujo, Sailik Sengupta, Jiyong Jang, \textbf{Adam Doup\'e}, Kevin W. Hamlen, and Subbarao Kambhampati, ``Software Deception Steering through Version Emulation,'' in \emph{Proceedings of the Hawaii International Conference on System Sciences}, Online, January, 2021.

\item \underline{Pradeep Kumar Duraisamy Soundrapandian}, Tiffany Bao, Jaejong Baek, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, Ruoyu Wang, and Gail-Joon Ahn, ``MuTent: Dynamic Android Intent Protection with Ownership-Based Key Distribution and Security Contracts,'' in \emph{Proceedings of the Hawaii International Conference on System Sciences}, Online, January, 2021.

\item \underline{Marzieh Bitaab}, \underline{Haehyun Cho}, Adam Oest, \underline{Penghui Zhang}, \underline{Zhibo Sun}, \underline{Rana Pourmohamad}, Dowoon Kim, Tiffany Bao, Ruoyu Wang, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``Scam Pandemic: How Attackers Exploit Public Fear through Phishing,'' in \emph{Proceedings of the Symposium on Electronic Crime Research (eCrime)}, November, 2020.

\item \underline{Efr\'en L\'opez Morales}, Carlos E. Rubio-Medrano, \textbf{Adam Doup\'e}, Yan Shoshitaishvili, Ruoyu Wang, Tiffany Bao, and Gail-Joon Ahn, ``HoneyPLC: A Next-Generation Honeypot for Industrial Control Systems,'' in \emph{Proceedings of the ACM Conference on Computer and Communications Security (CCS)}, November, 2020. (16.9\% acceptance rate.)

\item \underline{Adam Oest}, \underline{Penghui Zhang}, Brad Wardman, Eric Nunes, Jakub Burgis, Ali Zand, Kurt Thomas, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``Sunrise to Sunset: Analyzing the End-to-end Life Cycle and Effectiveness of Phishing Attacks at Scale,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, Boston, MA, August, 2020. (16.1\% acceptance rate.) \\
  \textbf{Distinguished Paper Award} \\
  \textbf{Second Place Internet Defense Prize}

\item \underline{Adam Oest}, \underline{Yeganeh Safaei}, \underline{Penghui Zhang}, Brad Wardman, Kevin Tyers, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``PhishTime: Continuous Longitudinal Measurement of the Effectiveness of Anti-phishing Blacklists,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, Boston, MA, August, 2020. (16.1\% acceptance rate.)

\item Rasoul Jahanshahi, \textbf{Adam Doup\'e}, and Manuel Egele, ``You shall not pass: Mitigating SQL Injection Attacks on Legacy Web Applications,'' in \emph{Proceedings of the ACM Symposium on Information, Computer and Communications Security (AsiaCCS)}, June, 2020.

\item Christopher Salls, Aravind Machiry, \textbf{Adam Doup\'e}, Yan Shoshitaishvili, Christopher Kruegel, and Giovanni Vigna, ``Exploring Abstraction Functions in Fuzzing,'' in \emph{Proceedings of the IEEE Conference on Communications and Network Security (CNS)}, June, 2020.

\item \underline{Haehyun Cho}, Jinbum Park, Donguk Kim, Ziming Zhao, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``SmokeBomb: Effective Mitigation Against Cache Side-channel Attacks on the ARM Architecture,'' in \emph{Proceedings of the Annual International Conference on Mobile Systems, Applications, and Services (MobiSys)}, Toronto, Canada, June 2020. (19\% acceptance rate.)

\item \underline{Faris Bugra Kokulu}, \underline{Ananta Soneji}, Tiffany Bao, Yan Shoshitaishvili, Ziming Zhao, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``Matched and Mismatched SOCs: A Qualitative Study on Security Operations Center Issues,'' in \emph{Proceedings of the ACM Conference on Computer and Communications Security (CCS)}, London, UK, November, 2019. (16\% acceptance rate.)

\item \underline{Huahong Tu}, \textbf{Adam Doup\'e}, Ziming Zhao, and Gail-Joon Ahn, ``Users Really Do Answer Telephone Scams,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, Santa Clara, CA, August 2019. (16\% acceptance rate.) \\
  \textbf{Distinguished Paper Award}

\item \underline{Erik Trickel}, Oleksii Starov, Alexandros Kapravelos, Nick Nikiforakis, and \textbf{Adam Doup\'e}, ``Everyone is Different: Client-side Diversification for Defending Against Extension Fingerprinting,'' in \emph{Proceedings of the USENIX Security Symposium (USENIX)}, Santa Clara, CA, August 2019. (16\% acceptance rate.)

\item \underline{Adam Oest}, \underline{Yeganeh Safaei}, \textbf{Adam Doup\'e}, Gail-Joon Ahn, Brad Wardman, and Kevin Tyers, ``PhishFarm: A Scalable Framework for Measuring the Effectiveness of Evasion Techniques Against Browser Phishing Blacklists,'' in \emph{Proceedings of the IEEE Symposium on Security and Privacy}, San Francisco, CA, May 2019. (12\% acceptance rate.)

 \item \underline{Penghui Zhang}, \underline{Haehyun Cho}, Ziming Zhao, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``iCORE: Continuous and Proactive Extrospection on Multi-core IoT Devices,'' in \emph{Proceedings of the ACM Symposium on Applied Computing (SAC)}, Limassol, Cyprus, April 2019. (24\% acceptance rate.)

\item \underline{Zhibo Sun}, Carlos E.
Rubio-Medrano, Ziming Zhao, Tiffany Bao, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``Understanding and Detecting Private Interactions in Underground Forums,'' in \emph{Proceedings of the ACM on Conference on Data and Application Security and Privacy (CODASPY)}, Dallas, TX, March 2019.

\item \underline{Haehyun Cho}, \underline{Penghui Zhang}, Donguk Kim, Jinbum Park, Choong-Hoon Lee, Ziming Zhao, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``Prime+Count: Novel Cross-world Covert Channels on ARM TrustZone,'' in \emph{Proceedings of the Annual Computer Security Applications Conference (ACSAC)}, Puerto Rico, December 2018.

\item Jaejong Baek, \underline{Sukwha Kyung}, \underline{Haehyun Cho}, Ziming Zhao, Yan Shoshitaishvili, \textbf{Adam Doup\'e}, and Gail-Joon Ahn, ``Wi Not Calling: Practical Privacy and Availability Attacks in Wi-Fi Calling,'' in \emph{Proceedings of the Annual Computer Security Applications Conference (ACSAC)}, Puerto Rico, December 2018.

\item \underline{Vaibhav Hemant Dixit}, \textbf{Adam Doup\'e}, Yan
  Shoshitaishvili, Ziming Zhao, and Gail-Joon Ahn, ``AIM-SDN:
  Attacking Information Mismanagement in SDN-datastores,'' in
  \emph{Proceedings of the ACM Conference on Computer and
    Communications Security (CCS)}, Toronto, Canada, October 2018. (16.6\% acceptance rate.)

\item \underline{Mike Mabey}, \textbf{Adam Doup\'e}, Ziming Zhao, and Gail-Joon Ahn, ``Challenges, Opportunities and a Framework for Web Environment Forensics,'' in \emph{Proceedings of the IFIP International Conference on Digital Forensics}, August 2018.


\item \underline{Adam Oest}, \underline{Yeganeh Safaei}, \textbf{Adam Doup\'e},
  Gail-Joon Ahn, Brad Wardman, and Gary Warner, ``Inside a Phisher's
  Mind: Understanding the Anti-phishing Ecosystem Through Phishing Kit
  Analysis,'' in \emph{Proceedings of the Symposium on Electronic
    Crime Research (eCrime)}, San Diego, May 2018.

\item \underline{Sai Prashanth Chandramouli}, Pierre-Marie Bajan,
  Christopher Kruegel, Giovanni Vigna, Ziming Zhao, \textbf{Adam Doup\'e}, and
  Gail-Joon Ahn, ``Measuring E-Mail Header Injections on the World
  Wide Web,'' in \emph{Proceedings of the ACM Symposium on Applied
    Computing (SAC)}, Pau, France, April 2018.

\item \underline{Sukwha Kyung}, \underline{Wonkyu Han},
  \underline{Naveen Tiwari}, \underline{Vaibhav Dixit},
  \underline{Lakshmi Srinivas}, Ziming Zhao, \textbf{Adam Doup\'e}, and
  Gail-Joon Ahn, ``HoneyProxy: Design and Implementation of
  Next-Generation Honeynet via SDN,'' in \emph{Proceedings of the IEEE
    Conference on Communications and Network Security (CNS)}, Las
  Vegas, NV, October 2017.

\item Sailik Sengupta, Satya Gautam Vadlamudi, Subbarao Kambhampati,
  \textbf{Adam Doup\'e}, Ziming Zhao, \underline{Marthony Taguinod},
  and Gail-Joon Ahn, ``A Game Theoretic Approach of Strategy
  Generation for Moving Target Defense in Web Applications,'' in
  \emph{Proceedings of the International Conference on Autonomous Agents
    and Multiagent Systems (AAMAS)}, Sao Paulo, May 2017.

\item Niall McLaughlin, Jesus Martinez del Rincon, BooJoong Kang,
  Suleiman Yerima, Paul Miller, Sakir Sezer, \underline{Yeganeh
    Safaei}, \underline{Erik Trickel}, Ziming Zhao, \textbf{Adam
    Doup\'e}, Gail-Joon Ahn, ``Deep Android Malware Detection,'' in
  \emph{Proceedings of the ACM on Conference on Data and Application
    Security and Privacy (CODASPY)}, Scottsdale, Arizona, March 2017.

\item \underline{Huahong Tu}, \textbf{Adam Doup\'e}, Ziming Zhao, and
  Gail-Joon Ahn, ``Toward Authenticated Caller ID Transmission: The
  Need for a Standardized Authentication Scheme in Q.731.3 Calling
  Line Identification Presentation,'' in \emph{Proceedings of the ITU
    Kaleidoscope}, Bangkok, Thailand, November 2016. \\
  \textbf{Best Paper Award}

\item \underline{Mike Mabey}, \textbf{Adam Doup\'e}, Ziming Zhao, and
  Gail-Joon Ahn, ``dbling: Identifying Extensions Installed on
  Encrypted Web Thin Clients,'' in \emph{Proceedings of the Digital
    Forensics Research Conference (DFRWS)}, Seattle, WA, August 2016.

\item \underline{Wonkyu Han}, Hongxin Hu, Ziming Zhao, \textbf{Adam
  Doup\'e}, Gail-Joon Ahn, Kuang-Ching Wang and Juan Deng,
  ``State-aware Network Access Management for Software-Defined
  Networks,'' in \emph{Proceedings of the ACM Symposium on Access
    Control Models and Technologies (SACMAT)}, Shanghai, China, June
  2016.

\item \underline{Kevin Liao}$^*$, Ziming Zhao, \textbf{Adam Doup\'e},
  and Gail-Joon Ahn, ``Behind Closed Doors: Measurement and Analysis
  of CryptoLocker Ransoms in Bitcoin,'' in \emph{Proceedings of the
    Symposium on Electronic Crime Research (eCrime)}, Toronto, Canada,
  June 2016.

\item \underline{Huahong Tu}, \textbf{Adam Doup\'e}, Ziming Zhao, and
  Gail-Joon Ahn, ``SoK: Everyone Hates Robocalls: A Survey of
  Techniques against Telephone Spam,'' in \emph{Proceedings of the
    IEEE Symposium on Security and Privacy}, San Jose, CA, May 2016.
  (13.3\% acceptance rate.)

\item \underline{Yiming Jing}, Gail-Joon Ahn, \textbf{Adam Doup\'e},
  and Jeong Hyun Yi, ``Checking Intent-based Communication in Android
  with Intent Space Analysis,'' in \emph{Proceedings of the ACM
    Symposium on Information, Computer and Communications Security
  (AsiaCCS)}, Xi’an, China, May 2016. (20.9\% acceptance
  rate.)

\item Satya Gautam Vadlamudi, Sailik Sengupta, \underline{Marthony
  Taguinod}, Ziming Zhao, \textbf{Adam Doup\'e}, Gail-Joon Ahn and
  Subbarao Kambhampati, ``Moving Target Defense for Web Applications
  using Bayesian Stackelberg Games (Extended Abstract),'' in
  \emph{Proceedings of the International Conference on Autonomous
    Agents and Multiagent Systems (AAMAS)}, Singapore, May 2016.

\item Vitor Afonso, Antonio Bianchi, Yanick Fratantonio, \textbf{Adam
  Doup\'e}, Mario Polino, Paulo de Geus, Christopher Kruegel, and
  Giovanni Vigna, ``Going Native: Using a Large-Scale Analysis of
  Android Apps to Create a Practical Native-Code Sandboxing Policy,''
  in \emph{Proceedings of the ISOC Network and Distributed System
    Security Symposium (NDSS)}, San Diego, CA, February 2016. (15.4\%
  acceptance rate.)

\item \underline{Carlos E. Rubio-Medrano}, Ziming Zhao, \textbf{Adam
  Doup\'e}, and Gail-Joon Ahn, ``Federated Access Management for
  Collaborative Network Environments: Framework and Case Study,'' in
  \emph{Proceedings of the ACM Symposium on Access Control Models and
    Technologies (SACMAT)}, Vienna, Austria, June 2015. (28.8\%
  acceptance rate.)

\item Yan Shoshitaishvili, Luca Invernizzi, \textbf{Adam Doup\'e}, and
  Giovanni Vigna, ``Do You Feel Lucky? A Large-Scale Analysis of
  Risk-Rewards Trade-Offs in Cyber Security,'' in \emph{Proceedings of
    the ACM Symposium on Applied Computing (SAC 2014)}, Gyeongju,
  Korea, March 2014.

\item \textbf{Adam Doup\'e}, Weidong Cui, Mariusz H. Jakubowski,
  Marcus Peinado, Christopher Kruegel, and Giovanni Vigna, ``deDacota:
  Toward Preventing Server-Side XSS via Automatic Code and Data
  Separation,'' in \emph{Proceedings of the 20th ACM Conference on
    Computer and Communications Security (CCS)}, Berlin, Germany,
  November 2013. (19.8\% acceptance rate.)

\item \textbf{Adam Doup\'e} and Janet L. Kayfetz, ``Writing Groups in
  Computer Science Research Labs,'' in \emph{Proceedings of the
    Frontiers in Education Conference (FIE 2013)}, Oklahoma City, OK,
  October 2013.

\item \underline{Pierre Payet}, \textbf{Adam Doup\'e}, Christopher
  Kruegel, and Giovanni Vigna, ``EARs in the Wild: Large-Scale
  Analysis of Execution After Redirect Vulnerabilities,'' in
  \emph{Proceedings of the ACM Symposium on Applied Computing (SAC
    2013)}, Coimbra, Portugal, March 2013.

\item \textbf{Adam Doup\'e}, Ludovico Cavedon, Christopher Kruegel,
  and Giovanni Vigna, ``Enemy of the State: A State-Aware Black-Box
  Web Vulnerability Scanner,'' in \emph{Proceedings of the 21st USENIX
    conference on Security (USENIX 2012)}, Bellevue, WA, August 2012.
  (19.4\% acceptance rate.) \\
  \textbf{Outstanding Publication Award in Computer
  Science, UC Santa Barbara}

\item \textbf{Adam Doup\'e}, Manuel Egele, Benjamin Caillat, Gianluca
  Stringhini, Gorkem Yakin, Ali Zand, Ludovico Cavedon, and Giovanni
  Vigna, ``Hit 'em Where it Hurts: A Live Security Exercise on Cyber
  Situational Awareness,'' in \emph{Proceedings of the Annual Computer
    Security Applications Conference (ACSAC 2011)}, Austin, TX,
  December 2011. (20\% acceptance rate.)

\item \textbf{Adam Doup\'e}, Bryce Boe, Christopher Kruegel, and
  Giovanni Vigna, ``Fear the EAR: Discovering and Mitigating Execution
  After Redirect Vulnerabilities,'' in \emph{Proceedings of the 18th
    ACM Conference on Computer and Communications Security (CCS
    2011)}, Chicago, IL, October 2011. (14\% acceptance rate.)

\item \textbf{Adam Doup\'e}, Marco Cova, and Giovanni Vigna, ``Why
  Johnny Can't Pentest: An Analysis of Black-box Web Vulnerability
  Scanners,'' in \emph{Proceedings of the Seventh Conference on
    Detection of Intrusions and Malware \& Vulnerability Assessment
    (DIMVA 2010)}, Bonn, Germany, July 2010. (34\% acceptance rate.)

\end{etaremune}

\subsection{Workshop Papers with Proceedings (refereed)}

\begin{etaremune}

\item Sana Habib,  Tiffany Bao,  Yan Shoshitaishvili, and  \textbf{Adam Doup\'e}, ``Mitigating Threats Emerging from the Interaction between SDN Apps and SDN (Configuration) Datastore,'' in \emph{Proceedings of the ACM Cloud Computing Security Workshop (CCSW)}, November, 2022.

\item \underline{Haehyun Cho}, Jinbum Park, Joonwon Kang, Tiffany Bao, Ruoyu (Fish) Wang, Yan Shoshitaishvili, Adam Doup\'e, and Gail-Joon Ahn, ``Exploiting Uses of Uninitialized Stack Variables in Linux Kernels to Leak Kernel Pointers,'' in \emph{Proceedings of the USENIX Workshop on Offensive Technologies (WOOT)}, August, 2020.

\item \underline{Mauricio Gutierrez}, Ziming Zhao, \textbf{Adam Doup\'e}, Yan Shoshitaishvili, and Gail-Joon Ahn , ``CacheLight: Defeating the CacheKit Attack,'' in \emph{Proceedings of the Workshop on Attacks and Solutions in Hardware Security (ASHES)}, Toronto, Canada, October 2018.

\item \underline{Vaibhav Dixit}, \underline{Sukwha Kyung}, Ziming
  Zhao, Adam Doupé, Yan Shoshitaishvili, and Gail-Joon Ahn,
  ``Challenges and Preparedness of SDN-based Firewalls,'' in
  \emph{Proceedings of the ACM International Workshop on Security in
    Software Defined Networks and Network Function Virtualization
    (SDN-NFV Sec)}, Tempe, AZ, March 2018.

\item Carlos E. Rubio-Medrano, \underline{Josephine Lamp}$^*$, \textbf{Adam
  Doup\'e}, Ziming Zhao, and Gail-Joon Ahn, ``Mutated Policies: Towards
  Proactive Attribute-based Defenses for Access Control,'' in
  \emph{Proceedings of the Workshop on Moving Target Defense (MTD)},
  Dallas, TX, October 2017.

\item \underline{Erik Trickel}, Francesco Disperati, Eric Gustafson,
  \underline{Faezeh Kalantari}, \underline{Mike Mabey},
  \underline{Naveen Tiwari}, \underline{Yeganeh Safaei}, \textbf{Adam
    Doup\'e}, and Giovanni Vigna, ``Shell We Play A Game?
  CTF-as-a-service for Security Education,'' in \emph{Proceedings of
    the USENIX Workshop on Advances in Security Education (ASE)},
  Vancouver, CA, August 2017.

\item Patrick Mutchler, \underline{Yeganeh Safaei}, \textbf{Adam
  Doup\'e}, and John Mitchell, ``Target Fragmentation in Android
  Apps,'' in \emph{Proceedings of the Mobile Security Technologies
    Workshop (MoST)}, San Jose, CA, May 2016.

\item \underline{Wonkyu Han}, Ziming Zhao, \textbf{Adam Doup\'e}, and
  Gail-Joon Ahn, ``HoneyMix: Toward SDN-based Intelligent Honeynet,''
  in \emph{Proceedings of the ACM International Workshop on Security
    in Software Defined Networks and Network Function Virtualization
    (SDN-NFV Sec)}, New Orleans, LA, March 2016.

\item \underline{Carlos E. Rubio-Medrano}, \underline{Josephine
  Lamp}$^*$, \underline{Marthony Taguinod}, \textbf{Adam Doup\'e},
  Ziming Zhao, and Gail-Joon Ahn, ``Position Paper: Towards a Moving
  Target Defense Approach for Attribute-based Access Control,'' in
  \emph{Proceedings of the ACM Workshop on Attribute Based Access
    Control (ABAC)}, New Orleans, LA, March 2016.

\item Patrick Mutchler, \textbf{Adam Doup\'e}, John Mitchell,
  Christopher Kruegel, and Giovanni Vigna, ``A Large-Scale Study of
  Mobile Web App Security,'' in \emph{Proceedings of the Mobile
    Security Technologies Workshop (MoST)}, San Jose, CA, May 2015. \\
  \textbf{Best Paper Award}

\item Giovanni Vigna, Kevin Borgolte, Jacopo Corbetta, \textbf{Adam
  Doup\'e}, Yanick Fratantonio, Luca Invernizzi, Dhilung Kirat, and
  Yan Shoshitaishvili, ``Ten Years of iCTF: The Good, The Bad, and The
  Ugly,'' in \emph{Proceedings of the USENIX Summit on Gaming, Games
  and Gamification in Security Education (3GSE)}, San Diego, CA, August
  2014.

\end{etaremune}

\subsection{Book Chapters}

\begin{etaremune}

\item Gail-Joon Ahn, \textbf{Adam Doup\'e}, Ziming Zhao, and
  \underline{Kevin Liao}$^*$, ``Ransomware and cryptocurrency: Partners in
  crime,'' book chapter in Thomas J.\ Holt, Ed., \emph{Cybercrime
    Through an Interdisciplinary Lens}, pp.\ 105--126, Routledge
  Studies in Crime and Society, Taylor \& Francis Publishers, 2016.

\end{etaremune}

\subsection{Invited Papers}

\begin{etaremune}

\item \underline{Ajay Modi}, \underline{Zhibo Sun}, \underline{Anupam
  Panwar}, \underline{Tejas Khairnar}, Ziming Zhao, \textbf{Adam
  Doup\'e}, and Gail-Joon Ahn, ``Towards Automated Threat Intelligence
  Fusion,'' in \emph{Proceedings of the IEEE International Conference
    on Collaboration and Internet Computing (CIC)}, November 2016.

\item \underline{Marthony Taguinod}, \textbf{Adam Doup\'e}, Ziming
  Zhao, and Gail-Joon Ahn, ``Toward a Moving Target Defense for Web
  Applications,'' in \emph{Proceedings of the IEEE International
    Conference on Information Reuse and Integration (IRI)}, San
  Francisco, CA, August 2015.
\end{etaremune}

\subsection{Patent Activity}

\begin{etaremune}

  \item \underline{Huahong Tu}, \textbf{Adam Doup\'e}, Ziming Zhao,
    and Gail-Joon Ahn, ``Systems and Methods of Authenticating Caller
    Identity and Call Request Header Information for Outbound
    Telephony Communications,'' \emph{Patent US10447481B2}, 2019.

  \item Weidong Cui, \textbf{Adam Doup\'e}, Mariusz Jakubowski, and Marcus
    Peinado, ``Automatic Code and Data Separation of Web
    Application,'' \emph{Patent US9774620B2}, 2017.

\end{etaremune}

\section{Invited Talks}

\begin{etaremune}

\item ``Wild Wild Phish: Phrontiers in the Phight Against Phishing'' Keynote at the SecWeb Workshop, May, 2022.
  
\item ``Scam Pandemic: How Attackers Exploit Public Fear through Phishing,'' Invited talk for the FTC, July, 2021.

\item ``Cybersecurity, ASU, and You,'' Invited talk for the GenCyber camp for High Schoolers, June, 2021.

  \item ``Where Have All the Phishers Gone?'' Keynote at the Workshop on Measurements, Attacks, and Defenses for the Web (MADWeb), February, 2021.

  \item Moderated the ``Scaling the Academic Security Community'' panel at the ACM Conference on Computer and Communications Security, November, 2019.

  \item ``History and Future of Automated Vulnerability Analysis,'' Junior Keynote at ACM Symposium on Access Control Models and Technologies (SACMAT), June 2019.

  \item Participated in the ``Browsers and Security'' panel at the Workshop on Measurements, Attacks and Defenses for the Web (MADWeb), February 2019.

  \item ``Event-drivel Models and Security Research,'' Invited joint talk (with Fish Wang) for NETCOM Command Strategy Group, Sierra Vista, AZ, January 2019.

  \item ``The Effectiveness of Telephone Phishing Scams and Possible Solutions,''
    Invited talk at University of Illinois at Chicago, Chicago, IL, January 2018.

  \item ``Hack like a Human: Using Inductive Reverse Engineering for Black-Box Web Vulnerability Analysis,'' Invited talk at UC Santa Barbara, Santa Barbara, CA, November 2017.

  \item Participated in the ``Education and Workforce'' panel at the
    ASU Congressional Conference on Cybersecurity, August 2017.

  \item Participated in the ``Rigor in Experimentation'' panel at the
    USENIX Workshop on Cyber Security Experimentation and Test (CSET),
    August 2017.

  \item ``The Effectiveness of Telephone Phishing Scams and Possible Solutions,''
    Invited talk at University College London, London, UK, June
    2017.

  \item ``Everybody Hates Robocalls: What Can We Do About It?,''
    Invited talk at Stony Brook University, Stony Brook, NY, April
    2017.

  \item Moderated the ``Trustworthy Data Science'' panel at the ACM
    Conference on Data and Applications Security and Privacy
    (CODASPY), March 2017.

  \item ``Large-Scale Security Analysis of Android Applications,''
    Invited talk for the 3rd International Symposium on Mobile
    Security (MSEC 2016), December 2016.

  \item Moderated the ``Security Competitions'' panel at the USENIX
    Security Symposium, August 2016.

  \item ``A Computer in Every Pocket: Securing Mobile Applications,''
    Invited talk by Dr.\ Jennifer Hackney Price, ASU West, September
    2016.

  \item ``Everything You've Ever Wanted to Know About Black-Box Web
    Vulnerability Scanners (But Were Afraid to Ask),'' Invited talk,
    Open Web Application Security Project (OWASP) Phoenix Chapter,
    June 2016.

  \item ``Using Static Analysis to Tame the Wild Wild Web,'' Invited
    talk at Georgia Tech, Georgia, AL, February 2015.

  \item ``Into the Mind of the Hacker,'' Three hour workshop at UC
    Santa Barbara by request of Web Standard Group, Santa Barbara, CA,
    April 2012.

  \item ``Fear the EAR: Discovering and Mitigating Execution After
    Redirect Vulnerabilities,'' Invited talk at Raytheon, Santa
    Barbara, CA, October 2011.

\end{etaremune}

\section{Service}

\subsection{Program Committee}
\cvitem{2025}{IEEE Symposium on Security and Privacy (Oakland)}
\cvitem{2025}{Workshop on Binary Analysis Research (BAR)}
\cvitem{2024}{ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2024}{International Symposium on Research in Attacks, Intrusions and Defenses (RAID)}
\cvitem{2024}{USENIX Security Symposium (USENIX)}
\cvitem{2024}{IEEE Symposium on Security and Privacy (Oakland)}
\cvitem{2024}{Workshop on Binary Analysis Research (BAR)}
\cvitem{2022}{ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2022}{USENIX Security Symposium (USENIX)}
\cvitem{2022}{Workshop on Measurements, Attacks, and Defenses for the Web (MADWeb)}
\cvitem{2022}{Network and Distributed System Security Symposium (NDSS)}
\cvitem{2021}{The Web Conference (WWW)}
\cvitem{2021}{European Workshop on Systems Security (EuroSec)}
\cvitem{2021}{Workshop on Measurements, Attacks, and Defenses for the Web (MADWeb)}
\cvitem{2021}{Network and Distributed System Security Symposium (NDSS)}
\cvitem{2021}{USENIX Security Symposium (USENIX)}
\cvitem{2021}{IEEE Symposium on Security and Privacy}
\cvitem{2020}{Annual Computer Security Applications Conference (ACSAC)}
\cvitem{2020}{SecWeb Workshop (SecWeb)}
\cvitem{2020}{ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2020}{Workshop on Measurements, Attacks, and Defenses for the Web (MADWeb)}
\cvitem{2020}{Network and Distributed System Security Symposium (NDSS)}
\cvitem{2020}{USENIX Security Symposium (USENIX)}
\cvitem{2020}{The Web Conference (WWW)}
\cvitem{2020}{ACM Symposium on Information, Computer and Communications Security (AsiaCCS)}
\cvitem{2019}{APWG Annual Symposium on Electronic Crime Research (eCrime)}
\cvitem{2019}{Conference on Detection of Intrusions and Malware \&
  Vulnerability Assessment (DIMVA)}
\cvitem{2019}{ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2020}{IEEE Symposium on Security and Privacy}
\cvitem{2019}{ACM Conference on Security and Privacy in Wireless and Mobile Networks (WiSec)}
\cvitem{2019}{USENIX Security Symposium (USENIX)}
\cvitem{2019}{IEEE Workshop on the Internet of Safe Things (SafeThings)}
\cvitem{2019}{The Web Conference (WWW)}
\cvitem{2019}{Workshop on Measurements, Attacks, and Defenses for the Web (MADWeb)}
\cvitem{2019}{Network and Distributed System Security Symposium (NDSS)}
\cvitem{2018}{Annual Computer Security Applications Conference (ACSAC)}
\cvitem{2018}{ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2019}{IEEE Symposium on Security and Privacy}
\cvitem{2018}{Conference on Detection of Intrusions and Malware \&
  Vulnerability Assessment (DIMVA)}
\cvitem{2018}{APWG Annual Symposium on Electronic Crime Research (eCrime)}
\cvitem{2018}{IEEE International Conference on Distributed Computing Systems (ICDCS)}
\cvitem{2018}{USENIX Security Symposium (USENIX)}
\cvitem{2018}{Network and Distributed System Security Symposium (NDSS)}
\cvitem{2017}{Annual Computer Security Applications Conference (ACSAC)}
\cvitem{2017}{ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2017}{Conference on Detection of Intrusions and Malware \&
  Vulnerability Assessment (DIMVA)}
\cvitem{2017}{USENIX Security Symposium (USENIX)}
\cvitem{2017}{ACM Symposium on Applied Computing (SAC)}
\cvitem{2016}{ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2016}{USENIX Security Symposium (USENIX)}
\cvitem{2016}{International Conference on Availability, Reliability and Security (ARES)}
\cvitem{2016}{International World Wide Web Conference (WWW)}
\cvitem{2016}{ACM Symposium on Applied Computing (SAC)}
\cvitem{2015}{ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2015}{USENIX Security Symposium (USENIX)}
\cvitem{2015}{International Conference on Availability, Reliability and Security (ARES)}
\cvitem{2015}{International Conference on Web Engineering (ICWE)}
\cvitem{2015}{OWASP AppSecEU}
\cvitem{2015}{International World Wide Web Conference (WWW)}
\cvitem{2013}{GreHack}

\subsection{Conference Reviewer}

\cvitem{2016}{Frontiers in Education (FIE)}
\cvitem{2015}{Frontiers in Education (FIE)}
\cvitem{2014}{Frontiers in Education (FIE)}
\cvitem{2013}{Frontiers in Education (FIE)}

\subsection{Journal Reviewer}

\cvlistitem{ACM Transactions on Architecture and Code Optimization}
\cvlistitem{ACM Transactions on the Web}
\cvlistitem{ACM Transactions on Information and System Security (TISSEC)}
\cvlistitem{Computers — Open Access Journal}
\cvlistitem{Future Generation Computer Systems}
\cvlistitem{IET Software}
\cvlistitem{IEEE Transactions on Information Forensics \& Security}
\cvlistitem{IEEE Transactions on Dependable and Secure Computing}
\cvlistitem{IEEE Transactions on Reliability}
\cvlistitem{IEEE/ACM Transactions on Networking}
\cvlistitem{Journal of Software Testing, Verification and Reliability
  (STVR)}

\subsection{Journal Organization}

\cvitem{2020--2024}{Associate Editor of IEEE Transactions on Dependable and Secure Computing (TDSC)}

\subsection{Conference Organization}

\cvitem{2025}{Program Chair for the Hot Topics in the Science of Security (HotSoS) Symposium}
\cvitem{2025}{Area Chair of The Web Conference (WWW)}
\cvitem{2024}{Program Co-Chair of the USENIX WOOT Conference on Offensive Technologies (WOOT)}
\cvitem{2024}{Area Chair of The Web Conference (WWW)}
\cvitem{2023}{Associate Chair of the IEEE Symposium on Security and Privacy}
\cvitem{2021}{Web Security Track Chair for the ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2019}{Program co-Chair for the Workshop on Forming an Ecosystem Around Software Transformation (FEAST)}
\cvitem{2019}{Panel Chair for the ACM Conference on Computer and Communications Security (CCS)}
\cvitem{2019}{Student Travel Grant Committee for the Network and Distributed System Security Symposium (NDSS)}
\cvitem{2018}{Student Travel Grant Committee for the Network and Distributed System Security Symposium (NDSS)}
\cvitem{2018}{Tutorial Chair for ACM Symposium on Information, Computer and Communications Security
  (AsiaCCS)}
\cvitem{2018}{Distinguished Paper Committee for USENIX Security Symposium (USENIX)}
\cvitem{2017}{Panel Chair for ACM Conference on Data and
  Application Security and Privacy (CODASPY)}
\cvitem{2015}{Poster Co-Chair for USENIX Security Symposium}
\cvitem{2012}{Chair of Graduate Student Workshop on Computing
  (GSWC), UC Santa Barbara. Raised record \$8,600 from industry,
  organized larger venue, ensured reviews were written, facilitated PC
  meeting, and hosted actual event.}
\cvitem{2011}{Industry Liaison for Graduate Student Workshop on
  Computing (GSWC), UC Santa Barbara. Raised record \$8,500 from
  industry sponsors Google, AppFolio, Lastline, Qualcomm, and
  Microsoft.}

\subsection{Proposal Reviewer}

\cvitem{2024}{NSF SaTC Panel Reviewer}
\cvitem{2021}{NSF SaTC Panel Reviewer}
\cvitem{2020}{NSF SaTC Panel Reviewer}
\cvitem{2019}{NSF SaTC Panel Reviewer}
\cvitem{2018}{NSF SaTC Panel Reviewer}
\cvitem{2018}{NSF SaTC-EDU Panel Reviewer}
\cvitem{2015}{NSF SaTC Panel Reviewer}

\subsection{Faculty Advisor for Student Groups}

\cvitem{2014--Present}{Faculty Advisor for ASU Hacking Club (formerly known as pwndevils), a student
  organization affiliated with the Center for Cybersecurity and
  Trusted Foundations. The group meets weekly to practice ethical
  hacking skills to compete in Capture the Flag competitions.}

\cvitem{2016--2022}{Faculty Advisor for AZ Saber, a student group
  dedicated to teaching people the basics of swordsmanship and
  safety.}

\cvitem{2015--2022}{Faculty Advisor for Software Developers
  Association (SoDA), the largest student organization in the Fulton
  Schools of Engineering}

\subsection{Department Service}

\cvitem{2024--Present}{Personnel Committee, Arizona State University}
\cvitem{2024}{Trustworthy and Secure Social Connectivity Search Committee \textbf{Chair}, Arizona State University}
\cvitem{2023--Present}{Graduate Program Committee, Arizona State University}
\cvitem{2022}{Cybersecurity, Computation, and Consensus Search Committee \textbf{Chair}, Arizona State University}
\cvitem{2019--2022}{Undergraduate Program Committee, Arizona State
  University}
\cvitem{2018}{Cybersecurity Faculty Search Committee \textbf{Chair}, Arizona State
  University}
\cvitem{2014--2018}{PhD Admissions Committee, Arizona State
  University}
\cvitem{2016}{Cybersecurity Faculty Search Committee, Arizona State
  University}
\cvitem{2015}{Cybersecurity Faculty Search Committee, Arizona State
  University}

\subsection{Advisory Board}

\cvitem{2017--2019}{Advisory board of the EPSRC UK project ``ACCEPT:
  Addressing Cybersecurity and Cybercrime via a co-Evolutionary
  aPproach to reducing human-relaTed risks''
  \url{http://accept.sccs.surrey.ac.uk}}

\subsection{Media Interactions}

\cvitem{January, 14, 2025}{``ASU cybercrime-fighter helps us compute with confidence.'' Interviewed in ASU News Q\&A about the Center for Cybersecurity and Trusted Foundations' mission and recent successes.}

\cvitem{September, 9, 2024}{``Cybersecurity team including students, faculty from ASU wins \$2 million in international contest.'' Live interview with KTAR News (92.3 FM) about the Shellphish qualifying for DARPA's AIxCC competition.}

\cvitem{October, 24, 2023}{``Cybersecurity threats that keep experts up at night.'' Featured in ASU News Q\&A interview for Cybersecurity Awareness Month discussing online vigilance and emerging threats like e-commerce scam sites.}

\cvitem{January, 31, 2022}{``Fortifying the foundations of cybersecurity.'' Quoted in ASU News article announcing the launch of ASU's new cybersecurity center, explaining the goal of keeping users and their data safe through research and education.}

\cvitem{July, 28, 2021}{``Equipping the next generation of cybersecurity professionals.'' Quoted in ASU News article about preparing the next generation of cybersecurity professionals at ASU.}

\cvitem{August, 27, 2020}{``Zoom bombings are still happening during virtual school. Why?'' Interviewed by Lily Altavena of Arizona Republic.}

\cvitem{August, 6, 2019}{``Hacking with elite white hats.'' Interviewed by Scott Seckel on DEF CON CTF.}

\cvitem{February, 6, 2019}{``Especialistas alertam para ligações robôs.'' Interviewed by GloboTV for Brazillian news piece on robocalls.}

\cvitem{September, 13, 2018}{``ASU cybersecurity professionals encourage students to join the field.'' Interviewed by the State Press regarding cybersecurity jobs.}

\cvitem{April, 4, 2018}{``You Can't Clean Up a Data Spill.'' Quoted by
  April Glaser for Slate on the Facebook data leaks.}

\cvitem{October, 10, 2017}{``ASU director testifies at Equifax Senate
  hearing.'' Interviewed by Ethan Millman for The State Press on the
  Equifax data breach.}

\cvitem{August, 28, 2017}{``Junk call nightmare flooded woman with
  hundreds of bizarre phone calls a day.'' Interviewed by Jon Brodkin
  for Ars Technica on our robocall and caller ID spoofing research.}

\cvitem{August, 15, 2017}{``How you can stop those annoying
  robocalls.'' Appearance on CBS WNCN (North Carolina) discussing our
  robocall research.}

\cvitem{August, 7, 2017} {``ASU engineer Adam Doup\'e looks to
  safeguard personal data through advanced automated vulnerability
  analysis tools.'' Interview with Erik Wirtanen on my CAREER award}

\cvitem{June, 19, 2017} {``ASU team tests `green padlock' solution to
  scam phone calls.'' Interviewed by Derek Staahl for 3TV and CBS 5
  for a story on our caller ID security indicator research}

\cvitem{June, 13, 2017} {``Receiving more robocalls than ever? An ASU
  researcher may have a solution.'' Interview with Leslie Minton on our
  telephony security research}

\cvitem{March, 8, 2017} {``Robocall ringing your cellphone? Here's
  what not to do.'' My PhD student Huahong (Raymond) Tu interviewed by
  Ian Schwartz for CBS 5 for a story on robocalls}

\cvitem{January, 31, 2017} {``Professors explain the flaws of a
  'password system' in a digital world.'' Interview by Aravind
  Sreenivasa for The State Press, ASU's student paper, on the state of
  password security}

\cvitem{January, 10, 2017} {``State computers hit with suspected
  malware attack.'' Interview with William Pitts for 12 News about
  recent reports of state of AZ HR computers infected with malware}

\cvitem{October, 19, 2016} {``How the FCC, the telecom industry and
  computer programmers are working to fight robocalls.'' My PhD
  student Huahong (Raymond) Tu interviewed by Larry Mantle for LA’s KPCC’s AirTalk radio program for a story on robocalls}

\cvitem{October, 4, 2016} {``Fed up with rising robocalls, millions
  say ‘Do Not Call’ list doesn’t work and want relief.'' My PhD
  student Huahong (Raymond) Tu quoted in The Orange Country Register for a story on robocalls by Lily Leung}

\cvitem{September, 23, 2016} {``Why is Yahoo hack so problematic?.'' Interview with Ryan Cody for 12 News about the impact of the Yahoo breach and why email security is so important.}

\cvitem{August, 29, 2016} {``Russian hack targets Arizona voter
  information.'' Interview with Brahm Resnik for 12 News about recent allegations of Russian hackers targeting Arizona voter registration.}

\cvitem{August, 29, 2016} {``Russian hackers tried to break into AZ
  voter database.'' Interview with Brahm Resnik for 12 News about recent allegations of Russian hackers targeting Arizona voter registration.}

\cvitem{July, 27, 2016} {``DNC email leak should be a lesson for all
  of us.'' Interview with Ryan Cody for 12 News about the importance of securing your personal email and tips to keep your personal email secure.}

\cvitem{March, 1, 2016} {``Software Development Association students
  compete, network and have fun.'' Story about the ASU Software Developer Association (SoDA) 2016 Coding Competition.}

\cvitem{February, 4, 2016} {``Arizona Department of Revenue IT Systems
  Vulnerable.'' Interview with Amber Kahwaji for Cronkite News about an AZ Department of Revenue Report on IT Vulnerabilities}

\cvitem{July, 27, 2015} {``Exclusive: MCAO talked about buying
  spyware.'' Interview with William Pitts for 12 News about details of the Hacking Team leaks.}

\cvitem{April, 22, 2015} {``Feds: Terrorist could hack your plane.'' Interview with William Pitts for 12 News about hacking airplanes.}



\section{Research Experience}

\cventry{2013 (Summer)}{Visiting PhD Student}{Stanford
  University}{Advisor: John C.\ Mitchell}{}{}

\cventry{2012 (Summer)}{Research Intern}{Microsoft Research}{Advisor:
  Weidong Cui}{}{}

\section{Industry Experience}

\cventry{2009--2010}{Software Developer Engineer}{Microsoft}{Developed
  as a team a C\# Microsoft Word plug-in to assist technical writers.
  Met critical deadlines in high-pressure situations}{}{}

\cventry{2008 (Summer)}{Software Developer Engineer
  Intern}{Microsoft}{Developed a C\# application that could save a
  technical writer documenting XML schemas 20 hours in 2 weeks} {}{}

\cventry{2007--2008}{Software Developer}{AT\&T Government
  Solutions}{Developed and maintained a large C++ desktop
  application}{}{}

\cventry{2005--2010}{Founder/Developer}{WootWatchers.com}{Founded
  WootWatchers.com using Ruby on Rails connecting to a MySQL backend.
  At its peak had 4,000 users}{}{}

\cventry{2004--2005}{Mobile Product Manager}{VCEL, Inc.}{Started off
  developing a client-server J2ME application. Then maintained and
  developed the server back-end using PHP}{}{}

\section{Capture the Flag Organization}


\cventry{2018--2022}{Founding Member}{Order of the Overflow}{Lead a group of hackers to organize the DEF CON Capture the Flag (CTF) competition, considered the ``Olympics'' of CTF. We host two competitions annually: DEF CON CTF Quals (which teams from all around the world play), and where the top teams from that competition compete in DEF CON CTF Finals, co-located with the DEF CON security conference.}{}{}

\section{Entrepreneurship}

\cventry{2024--Present}{Co-founder}{Pwn In Motion, LLC}{Productize open-source research prototypes for clients.}{}{}

\cventry{2023--Present}{Co-founder}{pwn.college, LLC}{Provide educational cybersecurity trainings. Finished Phase I STTR and currently in Phase II STTR, 30\% of which goes to ASU.}{}{}


\section{Teaching Experience}

\subsection{Instructor}

\cvitem{Fall 2024}{CSE 466 ``Computer Systems Security'' at ASU.
\textbf{4.51}/5 course evaluation and \textbf{4.7}/5 instructor evaluation from 7 of 50 enrolled students.}

\cvitem{Fall 2024}{CSE 466 ``Computer Systems Security'' at ASU.
\textbf{5}/5 course evaluation and \textbf{5}/5 instructor evaluation from 2 of 16 enrolled students.}

\cvitem{Fall 2024}{CSE 598 ``Applied Vulnerability Research'' at ASU.
\textbf{4.69}/5 course evaluation and \textbf{5}/5 instructor evaluation from 3 of 13 enrolled students.}

\cvitem{Spring 2024}{CSE 598 ``Advanced Software Exploitation'' at ASU.
\textbf{4.94}/5 course evaluation and \textbf{4.92}/5 instructor evaluation from 7 of 10 enrolled students.}

\cvitem{Fall 2023}{CSE 365 ``Introduction to Information Assurance'' at ASU.
\textbf{4.57}/5 course evaluation and \textbf{4.58}/5 instructor evaluation from 75 of 323 enrolled students.}

\cvitem{Fall 2023}{CSE 365 ``Introduction to Information Assurance'' at ASU.
\textbf{4.55}/5 course evaluation and \textbf{4.58}/5 instructor evaluation from 79 of 337 enrolled students.}

\cvitem{Spring 2022}{CSE 365 ``Introduction to Information Assurance'' at ASU.
\textbf{4.63}/5 course evaluation and \textbf{4.72}/5 instructor evaluation from 56 of 238 enrolled students.}

\cvitem{Spring 2021}{CSE 365 ``Introduction to Information Assurance'' at ASU.
\textbf{4.61}/5 course evaluation and \textbf{4.78}/5 instructor evaluation from 62 of 272 enrolled students.}

\cvitem{Spring 2020}{CSE 365 ``Introduction to Information Assurance'' at ASU.
\textbf{4.61}/5 course evaluation and \textbf{4.77}/5 instructor evaluation from 100 of 349 enrolled students.}

\cvitem{Fall 2019}{CSE 365 ``Introduction to Information Assurance'' at ASU.
\textbf{4.63}/5 course evaluation and \textbf{4.72}/5 instructor evaluation from 86 of 186 enrolled students.}

\cvitem{Fall 2018}{CSE 365 ``Introduction to Information Assurance'' at ASU.
\textbf{4.72}/5 course evaluation and \textbf{4.87}/5 instructor evaluation from 24 of 100 enrolled students.}

\cvitem{Spring 2018}{CSE 545 ``Software Security'' at ASU.
\textbf{4.66}/5 course evaluation and \textbf{4.78}/5 instructor evaluation from 56 of 107 enrolled students.}

\cvitem{Fall 2017}{CSE 465 ``Information Assurance'' at ASU.
\textbf{4.58}/5 course evaluation and \textbf{4.74}/5 instructor evaluation from 27 of 120 enrolled students.}

\cvitem{Spring 2017}{CSE 545 ``Software Security'' at ASU.
\textbf{4.72}/5 course evaluation and \textbf{4.82}/5 instructor evaluation from 92 of 139 enrolled students.}

\cvitem{Fall 2016}{CSE 340 ``Principles of Programming Languages'' at ASU.
\textbf{4.76}/5 course evaluation and \textbf{4.8}/5 instructor evaluation from 71 of 223 enrolled students.}

\cvitem{Spring 2016}{CSE 340 ``Principles of Programming Languages'' at ASU.
\textbf{4.5}/5 course evaluation and \textbf{4.88}/5 instructor evaluation from 32 of 119 enrolled students.}

\cvitem{Spring 2016}{CSE 545 ``Software Security'' at ASU.
\textbf{4.73}/5 course evaluation and \textbf{4.79}/5 instructor evaluation from 73 of 119 enrolled students.}

\cvitem{Fall 2015}{CSE 340 ``Principles of Programming Languages'' at ASU.
\textbf{4.46}/5 course evaluation and \textbf{4.74}/5 instructor evaluation from 92 out of the 204 students.}

\cvitem{Spring 2015}{Created CSE 591 ``Security and Vulnerability Analysis'' at ASU.
\textbf{4.73}/5 course evaluation and \textbf{4.89}/5 instructor evaluation from 48 of 63 enrolled students.}

\cvitem{Fall 2013}{Co-created and co-taught ``Recent Trends in
  Computing Research'' at University of California, Santa Barbara, a
  2-unit seminar graduate class.}

\subsection{Current Thesis Advisor (Academic Committee Chair)}

\cvitem{2015--Present}{Yeganeh Safaei (PhD Student)}
\cvitem{2016--Present}{Faris Kokulu (PhD Student)}
\cvitem{2019--Present}{Ananta Soneji (PhD Student)}
\cvitem{2019--Present}{Wil Gibbs (PhD Student)}
\cvitem{2022--Present}{Zhuoer Lyu (PhD Student)}
\cvitem{2022--Present}{Zach Smith (PhD Student)}
\cvitem{2024--Present}{Alemi Farhad (PhD Student)}
\cvitem{2024--Present}{Giorgi Arsenadze (PhD Student)}
\cvitem{2024--Present}{Davit Benashvili (PhD Student)}



\subsection{Prior PhD Advisor (Academic Committee Chair)}
\cvitem{2025}{Marzieh Bitaab (PhD) Dissertation: ``A Study of Fraudulent E-Commerce Website Modus Operandi.'' Amazon.}
\cvitem{2024}{Faezeh Kalantari (PhD) Dissertation: ``Safeguarding Users' Web Interactions.'' Fingerprint.}
\cvitem{2024}{Connor Nelson (PhD) Dissertation: ``Hacking the Learning Curve: Effective Cybersecurity Education at Scale.'' Research Software Engineer, ASU.}
\cvitem{2023}{Vivin Paliath (PhD) Dissertation: ``Modeling State to Improve Defensive Cyberattack Strategies.'' co-founder of startup Basata.}
\cvitem{2023}{Erik Trickel (PhD) Dissertation: ``Attacking Computer Security from the Perspective of Educators, Users, and Analysts.'' Assistant Teaching Professor, ASU.}
\cvitem{2023}{Zhibo (Eric) Sun (PhD) Dissertation: ``In the Light and in the Shadows:
Human-Centered Analysis in Cybercrime.'' Assistant Professor, Drexel University.}
\cvitem{2022}{Penghui Zhang (PhD) Dissertation: ``Treatments Against Sophisticated Phishing Attacks.'' Meta.}
\cvitem{2021}{Haehyun Cho (PhD) Dissertation: ``Exploiting and Mitigating Advanced Security Vulnerabilities.'' Assistant Professor, Soongsil University.}
\cvitem{2020}{Adam Oest (PhD) Dissertation: ``Leveraging Scalable Data Analysis to Proactively Bolster the Anti-Phishing Ecosystem.'' Paypal.}
\cvitem{2017}{Huahong Tu (PhD) Dissertation: ``From Understanding
  Telephone Scams to Implementing Authenticated Caller ID
  Transmission.'' Assistant Clinical Professor, University of Maryland.}
\cvitem{2017}{Michael Mabey (PhD) Dissertation: ``Forensic Methods and
  Tools for Web Environments.''}

\subsection{Prior Masters Advisor (Academic Committee Chair)}
\cvitem{2022}{Purv Rakeshkumar Chauhan (Masters) Thesis: ``Trapped in Transparency: Analyzing the Eﬀectiveness of Security Defenses in Real-World Scenarios.'' Nextiva.}
\cvitem{2020}{Jaswant Pakki (Masters) Thesis: ``Everything You Ever Wanted to Know About Bitcoin Mixers (But Were Afraid to Ask).'' Raytheon.}
\cvitem{2020}{Will Gibbs (Masters) Thesis: ``Natural Intent: The Use and Misuse of Intents in Android Applications.''}
\cvitem{2019}{Zackary Crosley (Masters) Thesis: ``Automated Reflection of CTF Hostile Exploits (ARCHES): Inductive Programming Techniques for Network Traffic Comprehension and Reflection.''}
\cvitem{2019}{Connor Nelson (Masters) Thesis: ``IRE: A Framework For Inductive Reverse Engineering.''}
\cvitem{2018}{Vaibhav Hemant Dixit (Masters) Thesis: ``Threats and Defenses in SDN Control Plane.''}
\cvitem{2018}{James Keith Hutchins (Masters) Thesis: ``FrozenNode: Static Linking of Node.js Applications.''}
\cvitem{2017}{Marthony T. Taguinod (Masters) Thesis: ``Moving Target Defense Framework for Web Applications.''}
\cvitem{2017}{Ashwath Anand (Masters) Thesis: ``Threats, Countermeasures, and Research Trends for BLE-Based IoT Devices.''}
\cvitem{2017}{Gerard Pinto (Masters) Thesis: ``Shadow Phone
  and Ghost SIM: A Step toward Geo-Location Anonymous Calling in
  GSM.'' First job at IBM.}
\cvitem{2017}{Tejas Khairnar (Masters)
  Thesis: ``Next Generation Black-Box Web Application Vulnerability
  Analysis Framework.''}
\cvitem{2016}{Sai Chandramouli (Masters)
  Thesis: ``E-Mail Header Injections: An Analysis of the World Wide
  Web.'' First job at Amazon.}

\subsection{Prior Undergraduate Thesis Advisor}
\cvitem{2017}{Kevin Liao (Undergraduate) Thesis: ``Toward
  Inductive Reverse Engineering of Web Applications.'' PhD Student at
  UIUC.}

%% \subsection{Academic Committee Member}

%% \cvitem{}{\textbf{PhD}}
%% \cvitem{2015--Present}{Sandeep Pisharody, PhD.}
%% \cvitem{2015--Present}{Abdullah O. Alshalan, PhD.}
%% \cvitem{2016--2017}{Loretta Cheeks, PhD.}
%% \cvitem{2014--2016}{Carlos Rubio, PhD.}
%% \cvitem{2014--2016}{Wonkyu Han, PhD.}
%% \cvitem{2015--2016}{Michael Jonas, PhD.}
%% \cvitem{2014--2015}{Yiming Jing, PhD.}
%% \cvitem{2014--2015}{Priyanka Bagade, PhD.}


%% \cvitem{}{\textbf{Masters}}
%% \cvitem{2016--Present}{Sukwaha Kyung}
%% \cvitem{2017--Present}{Bhakti Bohara}
%% \cvitem{2017}{Anupam Panwar}
%% \cvitem{2017}{Ajay Modi}
%% \cvitem{2016}{Abhijeet Srivastava}
%% \cvitem{2015}{Jeremy Whitaker}
%% \cvitem{2015}{Clinton D'souza}
%% \cvitem{2014}{Narasimha Gollapudi}
%% \cvitem{2014}{James Holmes}
%% \cvitem{2014}{Michael Sanchez}

%% \cvitem{}{\textbf{Undergraduate Honors Thesis}}
%% \cvitem{2016--2018}{Josie Lamp}
%% \cvitem{2014--2018}{Daniel Martin}
%% \cvitem{2017}{Nathaniel Vaughan}
%% \cvitem{2016}{John Robertson}
%% \cvitem{2014}{Ryan Torrence}


\end{document}
